SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-26 scipy-1.0/paper.tex
Minor update to Maintainers section based on comment of @mdhaber.

\textbf{Maintainers and contributors}
The SciPy project has approximately 15 active maintainers (people who review
others' contributions, and in general do everything needed to ensure that
the software and the project move forward).  It also has an additional ~100
unique contributors for every 6-monthly release cycle.  Maintainers are
critical to the health of the project\cite{eghbal2016}; they enable contributions
from a much larger group, and their skills and efforts largely determine how
fast the project moves forward.  Anyone with the interest and skills can become
a maintainer; the SciPy Developer Guide provides guidance on how to do that.

>>>>

\textbf{Maintainers and contributors}
The SciPy project has approximately 15 active maintainers - people who review
others' contributions, and in general do everything needed to ensure that
the software and the project move forward. Maintainers are critical to the
health of the project\cite{eghbal2016}; their skills and efforts largely
determine how fast the project moves forward, and they enable contributions
from a much larger group. Accordingly, the project also has an additional
~100 unique contributors for every 6-monthly release cycle. Anyone with the
interest and skills can become a contributor or maintainer; the SciPy
Developer Guide provides guidance on how to do that.
